Effects of CHILDREN's programs

### 2020-02-25 paper.Rnw
complied with most formal requirements

\documentclass[12pt, a4paper]{article}
\usepackage{lscape}
\usepackage{graphicx}
\usepackage[utf8]{inputenc}
\usepackage[backend=biber, bibstyle=apa, citestyle=authoryear]{biblatex}
\usepackage{floatrow}
\usepackage[hidelinks]{hyperref}
\usepackage{rotating}
% \usepackage[authoryear]{natbib}
% \bibliographystyle{apalike}
\usepackage{mathtools}
\usepackage[onehalfspacing]{setspace}
\usepackage[left = 72 pt, right = 72 pt]{geometry}

@@

\title{Effects of CHILDREN's programs}
\author{Laura Huber, Laura Jepsen, Jonathan Kirschner, Rafael Schütz, Yannick Zurl}
\date{27th February 2020}

@@

\begin{titlepage}
\maketitle
\end{titlepage}

@@

Examples\\

Equation with\\

@@

Regression fit ouput with texreg

@@

<<Grants Regressions, echo=FALSE, results='asis', message=FALSE>>=

lm_ms = readRDS("./ANALYSIS/Tables/mealsNo_sub.lm.Rds")
lm_ts = readRDS("./ANALYSIS/Tables/tripsNo_sub.lm.Rds")
#outlier meals
#outlier trips 
#impute meals
#imputetrips

texreg(list(lm_ms, lm_ts), caption = "Grants Regressions", custom.model.names = c("Number of Meals", "Number of Trips"))
@

\begin{figure}
  \caption{Health Outcomes versus Healthy Meals}
  \label{Health_Plots}
<<Health Regressions percentageplots, echo=FALSE, message=FALSE>>=
Health_percentageplots <- readRDS("./ANALYSIS/GRAPHS/PAPER/Health_percentageplots.Rds")
print(Health_percentageplots)
@
\floatfoot{DGECriteriaNo is an index that captures how healthy the meals in an organization are. It is based on the criteria of the German Nutrition Society (Deutsche Gesellschaft für Ernährung). According to information from CHILDREN, they ask the organizations to send them their menus. An ecotrophologist collaborating with CHILDREN assesed the menus. In its yearly surveys CHILDREN asks about three variables closley related to a healthy diet. These are the degree to which beneficiaries: are healthier (lessIll\_ordered), have a growing appreciation for a healthier diet (dietaryKnowledge\_ordered), and have increased their knowledge about what constitutes a healthy diet (appreciateHealthy\_ordered).
The x-axis plots the index for a healthy diet. The y-axis displays the share of organizarions in each category of the health outcome. The possible values are: all(coded as 4), most (3), some (2), few (1), and none (coded as 0). For example, if an organization says that most beneficiaries are healthier, then this would be coded as 3.}
\end{figure}

<<Health Regressions, echo=FALSE, results='asis', message=FALSE>>=

@@

lm_lDGE = readRDS("./ANALYSIS/Tables/lessIll_DGE_scaled.lm.Rds")
lm_dDGE = readRDS("./ANALYSIS/Tables/dietaryKnowledge_DGE_scaled.Rds")
lm_aDGE = readRDS("./ANALYSIS/Tables/appreciateHealthy_DGE_scaled.Rds")

@@

lm_elDGE = readRDS("./ANALYSIS/Tables/Expand_LessIll_scaled.Rds")

stargazer(lm_dDGE, lm_aDGE, title = "Regression outcome: Health", align = TRUE)
@
<<Chance Equality Regressions, echo=FALSE, results='asis', message=FALSE>>=

lm_s = readRDS("./ANALYSIS/Tables/selfworth.lm.Rds") #weighted
lm_d = readRDS("./ANALYSIS/Tables/dayToDaySkills.lm.Rds") #weighted
lm_ss = readRDS("./ANALYSIS/Tables/selfworth_scaled.Rds") #standardized
lm_ds = readRDS("./ANALYSIS/Tables/dayToDaySkills_scaled.lm.Rds") #standardized

stargazer(lm_s, lm_d, lm_ss, lm_ds, title = "Regression outcome: Chance Equality", align = TRUE)
@

>>>>

\documentclass[12pt, a4paper, titlepage]{article}
\usepackage{lscape}
\usepackage{graphicx}
\usepackage[utf8]{inputenc}
\usepackage[backend=biber, bibstyle=apa, citestyle=authoryear]{biblatex}
\usepackage{floatrow}
\usepackage[hidelinks]{hyperref}
\usepackage{rotating}
% \usepackage[authoryear]{natbib}
% \bibliographystyle{apalike}
\usepackage{mathtools}
\usepackage[onehalfspacing]{setspace}
\usepackage[left = 2.5cm, top = 2.5cm, right = 2.5cm, bottom = 2.0cm]{geometry}

% 1.5 spacing in Word is about this in LaTeX
% https://tex.stackexchange.com/questions/65849/confusion-onehalfspacing-vs-spacing-vs-word-vs-the-world

\linespread{1.25}

@@

% multiple authors
% https://tex.stackexchange.com/questions/4805/whats-the-correct-use-of-author-when-multiple-authors

\title{Effects of CHILDREN's programs}
\author{
Laura Huber\\
\texttt{11111111}
\and
Laura Jepsen\\
\texttt{11111111}
\and
Jonathan Kirschner\\
\texttt{11724530}
\and
Rafael Schütz\\
\texttt{11574909} 
\and 
Yannick Zurl\\
\texttt{11111111}
\and
Studentisches Praxisprojekt zur Empirischen Wirtschaftsforschung PaRE3To\\
\and
Ludwig-Maximilians-Universität Munich
}

% Winter Term 2019/20\\

\date{27th February 2020}

@@

% \begin{titlepage}
\maketitle
% \end{titlepage}

@@

\begin{abstract} 
abstract on separate page
100 - 150 words
\end{abstract}

\section{Formal requirements}
all important information on title page, maybe use template\\
always name sources of tables and graphs\\
have to cite data sets\\

\section{Examples}

Equation with double index\\

@@

Regression fit output with texreg\\

<<mealsTripsSubsidyRegressions, echo=FALSE, results='asis'>>=
# , message=FALSE, warning=FALSE
# first, read in all Rds objects that you need
# 
mealsNo_sub.lm = readRDS("./ANALYSIS/Tables/mealsNo_sub.lm.Rds")
tripsNo_sub.lm = readRDS("./ANALYSIS/Tables/tripsNo_sub.lm.Rds")
#  
texreg(list(mealsNo_sub.lm, tripsNo_sub.lm))
@

@@

<<GrantsRegressions, echo=FALSE, results='asis', message=FALSE>>=

lm_ms = readRDS("./ANALYSIS/Tables/mealsNo_sub.lm.Rds")
lm_ts = readRDS("./ANALYSIS/Tables/tripsNo_sub.lm.Rds")
lm_ms_o = readRDS("./ANALYSIS/Tables/mealsNo_sub_ex.lm.Rds") #outlier meals
lm_ts_o = readRDS("./ANALYSIS/Tables/tripsNo_sub_ex.lm.Rds")#outlier trips 
lm_ms_i = readRDS("./ANALYSIS/Tables/mealsNo_sub_IM.lm.Rds")#impute meals
lm_ts_i = readRDS("./ANALYSIS/Tables/tripsNo_sub_IM.lm.Rds")#imputetrips

texreg(list(lm_ms, lm_ts, lm_ms_o, lm_ts_o, lm_ms_i, lm_ts_i), caption = "Grants Regressions", custom.model.names = c("MealsNo", "Trips No", "Meals No", "Trips No", "Meals No", "Trips No"))
@
Table 3: The first two columns are simple OLS models, in column 3 and 4 outliers are excluded and in column 5 and 6 data is imputed.

\begin{figure}
  \caption{Health Outcomes versus Healthy Meals}
  \label{Health_Plots}
<<HealthRegressionsPercentageplots, echo=FALSE, message=FALSE>>=
Health_percentageplots <- readRDS("./ANALYSIS/GRAPHS/PAPER/Health_percentageplots.Rds")
print(Health_percentageplots)
@
\floatfoot{DGECriteriaNo is an index that captures how healthy the meals in an organization are. It is based on the criteria of the German Nutrition Society (Deutsche Gesellschaft für Ernährung). According to information from CHILDREN, they ask the organizations to send them their menus. An ecotrophologist collaborating with CHILDREN assesed the menus. In its yearly surveys CHILDREN asks about three variables closley related to a healthy diet. These are the degree to which beneficiaries: are healthier (lessIll\_ordered), have a growing appreciation for a healthier diet (dietaryKnowledge\_ordered), and have increased their knowledge about what constitutes a healthy diet (appreciateHealthy\_ordered).
The x-axis plots the index for a healthy diet. The y-axis displays the share of organizarions in each category of the health outcome. The possible values are: all(coded as 4), most (3), some (2), few (1), and none (coded as 0). For example, if an organization says that most beneficiaries are healthier, then this would be coded as 3.}
\end{figure}

<<HealthRegressions, echo=FALSE, results='asis', message=FALSE>>=

@@

lm_lDGE = readRDS("./ANALYSIS/Tables/lessIll_DGE_scaled.lm.Rds")
lm_dDGE = readRDS("./ANALYSIS/Tables/dietaryKnowledge_DGE_scaled.Rds")
lm_aDGE = readRDS("./ANALYSIS/Tables/appreciateHealthy_DGE_scaled.Rds")
lDGE_i = readRDS("./ANALYSIS/Tables/lessIll_DGE_IM_scaled.lm.Rds")
dDGE_i = readRDS("./ANALYSIS/Tables/dietaryKnowledge_DGE_IM_scaled.lm.Rds")
aDGE_i = readRDS("./ANALYSIS/Tables/appreciateHealthy_DGE_IM_scaled.lm.Rds")

@@

lm_elDGE = readRDS("./ANALYSIS/Tables/Expand_LessIll_scaled.Rds")
elDGE_i = readRDS("./ANALYSIS/Tables/Expand_LessIll_IM_scaled.Rds")

texreg(list(lm_lDGE, lm_dDGE, lm_aDGE, lDGE_i, dDGE_i, aDGE_i), caption = "Health Outcome Regressions", custom.model.names = c("LessIll", "DietaryKnowledge", "AppreciateHealthy","LessIll", "DietaryKnowledge", "AppreciateHealthy"))
@

<<ChanceEqualityRegressions, echo=FALSE, results='asis', message=FALSE>>=

lm_s = readRDS("./ANALYSIS/Tables/selfworth.lm.Rds") #weighted
lm_d = readRDS("./ANALYSIS/Tables/dayToDaySkills.lm.Rds") #weighted
ts =
td =
lm_ss = readRDS("./ANALYSIS/Tables/selfworth_scaled.Rds") #standardized
lm_ds = readRDS("./ANALYSIS/Tables/dayToDaySkills_scaled.lm.Rds") #standardized 
tss =
tds =

texreg(list(), caption = "Equal Opportunities Regressions", custom.model.names = c())
@
